DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
trim whitespace
add optimal kernel width figure

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item add figure with optimal kernel widths
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item check that NN architectures and hyper-params are correctly reported
\end{itemize}
}
\newpage

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
	}
	\label{fig:architecture}
\end{figure}

@@

\subsection{Finding the optimal set of weights}
% !) summary the work of Khasanova -> No! to be put in section 2) Method
\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eq:belkin_weights}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors. Given $k$, we find the optimal $t$, a grid search is performed using \eqref{eq:mean equivariance error}.

>>>>

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
\end{itemize}
}
\newpage

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{figure_architecture_v3}
	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
	}
	\label{fig:architecture}
\end{figure}

@@

\subsection{Finding the optimal set of weights}

% 1) summary the work of Khasanova
\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{kernel_widths}
	\caption{
		Optimal kernel widths for various resolutions of the HEALPix grid.
	}
	\label{fig:kernel_widths}
\end{figure}

% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eq:belkin_weights}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.
